Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-06-01 results.tex
second draft of paper.

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic zones. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequence from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.

@@

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

>>>>

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic regions. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequences from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.

@@

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. The calculated parameters of each window was associated with the time of occurrence of the last event in sliding window. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

### 2016-06-01 seismicity.tex
second draft of paper.

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scale (reference). We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}. There are also some of data recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$. Although \citet{Deniz2010} defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude. We believe having those earthquakes, even with small error  in magnitude is important for estimating accurate  Gutenberge-Richter values.

@@

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.  \citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% as a threshold to select completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.

@@

\noindent
In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for three regions. Earthquakes with magnitude bigger than completeness magnitude are represented.

>>>>

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scale (reference). We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}. There are also some of data recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$.

@@

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include: 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.  \citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% as a threshold to select completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.

@@

\noindent
In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude bigger than completeness magnitude are represented.
